---
title: "SDS315.HW4"
author: "Aggie Angeles"
date: "2024-02-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# --- libraries
library(mosaic)
library(ggplot2)
library(tidyverse)
library(kableExtra)

# --- Data frames
GasPrice <- read.csv("gasprices.csv")
sClass <- read.csv("sclass.csv")
pilotNBC <- read.csv("nbc_pilotsurvey.csv")
eBay <- read.csv("ebay.csv")

# --- reproduce
set.seed(40)
```

## *Problem 1: Gas Prices in Austin (2016)* 
### *Part A - Direct Competition*


The claim is that gas stations charge more if they lack direct competition in sight. The data conveys that the difference of means (Yes Competition minus No Competition) is -0.0234, about 2 cents. There is a difference in means of somewhere between -0.0551 and 0.00741 dollars, about -6 cents to 1 cents. Based on the data, we can say with 95% confidence that there is little to no difference in gas stations charge more if they lack direction competition in sight compared to gas stations that do not lack direct competition on average. 

The difference in average price between direct competition and a lack of competition is not statistically significant at the 5% (0.05) level, because a 95% (0.95) confidence interval for that difference does contain zero in terms of the price. The evidence does not support the claim that gas stations charge more if they lack direct competition in sight. 


```{r echo = FALSE, mesage = FALSE, include=FALSE}
GasPrice %>%
  group_by(Competitors) %>%
  summarize(count = n())

mean(Price ~ Competitors, data=GasPrice)
diffmean(Price ~ Competitors, data=GasPrice)

BootComp = do(10000)*diffmean(Price ~ Competitors, data=resample(GasPrice))

confint(BootComp, level = 0.95)

```

```{r echo = FALSE, mesage = FALSE}

ggplot(BootComp) + 
  geom_histogram(aes(x=diffmean)) + labs( title = "Bootstrapped Confidence Interval: Price by Competition", x = "Difference in Means: Price by Competition")

```



### *Part B - Income and Price*

The claim is that the richer the area, the higher the gas prices.
The coefficient on income is actually positive: 1.248341e-06 or 0.000001 increase in gas prices with each additional dollar of income. Already, we see little to no correlation between the two variables.

We are 95% confident that the true population-wide slope of gas station price versus area income is somewhere between 6.481893e-07 (0.0000006) and 1.773643e-06	(0.000002) increase in gas prices with each additional dollar of income.

The linear regression between gas station price versus area income is not statistically significant at the 5% (0.05) level, because a 95% (0.95) confidence interval for the linear model does contain zero in the gas price. The evidence does not support the claim that the richer the area, the higher the gas prices.

```{r echo = FALSE, mesage = FALSE, include=FALSE}

lmPriceIncome = lm(Price ~Income, data=GasPrice)
coef(lmPriceIncome)
# cor. coeff 

BootIncome = do(10000)*lm(Price ~Income, data=resample(GasPrice))

confint(BootIncome, level = 0.95) %>% 
  filter(name == 'Income')
```
```{r echo = FALSE, mesage = FALSE}

ggplot(GasPrice) + 
  geom_jitter(aes(x=Income, y=Price), alpha=0.1) + 
  geom_smooth(aes(x=Income, y=Price), method='lm') + labs( title = "Price by Income")

```





### *Part C - Stoplights and Price*

The claim is that gas stations at stoplights charge more compared to gas stations not established in front of stoplights. The data conveys that the difference of means (Yes Stoplights minus No Stoplights) is -0.0033, about -1 cents. There is a difference in means of somewhere between -0.0388 and 0.0298 dollars, about -4 cents to 3 cents. Based on the data, we can say with 95% confidence that there is little to no difference in gas stations charge a established in front of a stoplight compared to gas stations that are not in near a stoplight on average.

The difference in average price between direct stoplight placement and no stoplight placement is not statistically significant at the 5% (0.05) level, because a 95% (0.95) confidence interval for that difference does contain zero in terms of the price. The evidence does not support the claim that gas stations at stoplights charge more compared to gas stations not established in front of stoplights. 


```{r echo = FALSE, mesage = FALSE, include=FALSE}

mean(Price ~ Stoplight, data=GasPrice)
diffmean(Price ~ Stoplight, data=GasPrice)

BootSpotlight = do(10000)*diffmean(Price ~ Stoplight, data=resample(GasPrice))

confint(BootSpotlight, level = 0.95)

```

```{r echo = FALSE, mesage = FALSE}

ggplot(BootSpotlight) + 
  geom_histogram(aes(x=diffmean)) + labs( title = "Bootstrapped Confidence Interval: Price by Stoplight", x = "Difference in Means: Price by Stoplight")

```




### *Part D - Highway Access and Price*

The claim is that gas stations with direct highway access charge more than gas stations without direct highway access. The data conveys that the difference of means (Yes Highways minus No Highways) is .0457, about 5 cents. Based on the data, we can say with 95% confidence that gas stations charge a bit more if they have direct highway access compared to gas stations that do not have direct highway access on average. There is a difference in means of somewhere between 0.0078 and 0.0821 dollars, about 1 cent to 8 cents. 

The difference in average price between direct highway access and no direct highway access is statistically significant at the 5% (0.05) level, because a 95% (0.95) confidence interval for that difference fails to contain zero in terms of the price. The evidence does support the claim that gas stations with direct highway access charge more than gas stations without direct highway access.



```{r echo = FALSE, mesage = FALSE, include=FALSE}

mean(Price ~ Highway, data=GasPrice)
diffmean(Price ~ Highway, data=GasPrice)

BootHighway = do(10000)*diffmean(Price ~ Highway, data=resample(GasPrice))

confint(BootHighway, level = 0.95)

```

```{r echo = FALSE, mesage = FALSE}
ggplot(BootHighway) + 
  geom_histogram(aes(x=diffmean)) + labs( title = "Bootstrapped Confidence Interval: Price by Highway Access", x = "Difference in Means: Price by Highway Access")


```






### *Part E - Shell or Not and Price*

The claim is that Shell charges more than all other non-Shell brands. The data conveys that the difference of means (Shell minus Not Shell) is 0.0274, about 3 cents. There is a difference in means of somewhere between -0.0107 and 0.0659 dollars, about -1 cent to 7 cents. Based on the data, we can say with 95% confidence that there is little to no difference in Shell gas stations charges and non-Shell gas stations in the greater Austin area. 

The difference in average price between Shell brands and non-Shell brands in the greater Austin area is not statistically significant at the 5% (0.05) level, because a 95% (0.95) confidence interval for that difference contain zero in terms of the price. The evidence does not support the claim that Shell charges more than all other non-Shell brands.



```{r echo = FALSE, mesage = FALSE, include=FALSE}

# --- mutate: Shell ( y or n )

GasPrice = GasPrice %>% 
  mutate(Shell = ifelse(Brand != "Shell", yes = FALSE, no = TRUE))

mean(Price ~ Shell, data=GasPrice)
diffmean(Price ~ Shell, data=GasPrice)

BootShell = do(10000)*diffmean(Price ~ Shell, data=resample(GasPrice))

ggplot(BootShell) + 
  geom_histogram(aes(x=diffmean)) 

confint(BootShell, level = 0.95)
```

```{r echo = FALSE, mesage = FALSE}
ggplot(BootShell) + 
  geom_histogram(aes(x=diffmean)) + labs( title = "Bootstrapped Confidence Interval: Price by Shell Branding", x = "Difference in Means: Price by Shell Branding")

```



## *Problem 2: Merecedes S-Class Vehicles* 
### *Part A - 2011 S-Class 63 AMGs*

Based on this Merecedes S-Class Vehicles data frame, 2011 S-Class 63 AMGS, on average, have a mileage of 28997.34. We state with a 95% confidence interval, the average mileage typically between 26304.8	to 31789.74. Because this confidence interval doesn’t contain zero, we can say that the mean is statistically significant at the 5% level.

```{r echo = FALSE, mesage = FALSE, include=FALSE}

amg <- sClass %>% 
  filter(year == 2011, trim == "63 AMG")

mean(~mileage, data = amg)

# average mileage 

bootMileage = do(10000)*mean(~mileage, data=resample(amg))

confint(bootMileage, level = .95)

```

```{r echo = FALSE, mesage = FALSE}
ggplot(bootMileage) +
  geom_histogram(aes(x=mean)) + labs( title = "Bootstrapped Confidence Interval: Mileage for 2011 S-Class 63 AMGS", x = "Mean Mileage")
```


### *Part B - 2014 S-Class 550s*


The proportion on average of black 2014 S-Class 550s Mercedes is 0.4348 for all 2014 S-Class 550s Mercedes. Based on our bootstrapped sample, we are 95% confident that the true population proportion of black 2014 S-Class 550s is somewhere between 0.4164 to	0.4530. Because this confidence interval doesn’t contain zero, we can say that the proportion is statistically significant at the 5% level.
	

```{r echo = FALSE, mesage = FALSE, include=FALSE}

fiveFifty <- sClass %>% 
  filter(year == 2014, trim == "550")

fiveFifty = fiveFifty %>% 
  mutate(isBlack = ifelse(color != "Black", yes = FALSE, no = TRUE))

prop(~isBlack, data = fiveFifty)

bootBlack = do(10000)*prop(~isBlack, data=resample(fiveFifty))

confint(bootBlack, level = .95)

```

```{r echo = FALSE, mesage = FALSE}
ggplot(bootBlack) +
  geom_histogram(aes(x=prop_TRUE)) + labs( title = "Bootstrapped Confidence Interval: Black or Not for 2014 S-Class 550s", x = "Proportion of Black ")
```



## *Problem 3:  NBC Pilot Viewer Survey* 
### *Part A - “Living with Ed” & “My Name is Earl” *


Using a bootstrapped 95% confidence interval of 10,000 difference in mean samples for viewers response to the Happiness question we are attempting to answer is whether the show Living with Earl or My Name is Earl makes viewers happier. Based on this, Ed makes viewers happier, on average, by a difference of .1491. We state with a 95% confidence interval, the average difference in happiness was typically between -0.3936193 to 0.1007705 (Earl - Ed). Because this confidence interval does contain zero, we cannot say that the mean is statistically significant at the 5% level.


```{r echo = FALSE, mesage = FALSE, include=FALSE}

earlEd <- pilotNBC %>% 
  filter( Show == "Living with Ed" | Show == "My Name is Earl")

mean(Q1_Happy ~ Show, data=earlEd)
diffmean(Q1_Happy ~ Show, data=earlEd)

bootHappy = do(10000)*diffmean(Q1_Happy ~ Show, data=resample(earlEd))

ggplot(bootHappy) + 
  geom_histogram(aes(x=diffmean))

confint(bootHappy, level = .95)

```

```{r echo = FALSE, mesage = FALSE}
ggplot(bootHappy) + 
  geom_histogram(aes(x=diffmean)) + labs( title = "Bootstrapped Confidence Interval: Living with Ed” & “My Name is Earl ", x = "Difference in Means: Happiness ")
```




### *Part B - “The Biggest Loser” & “The Apprentice: Los Angeles” *

Using a bootstrapped 95% confidence interval of 10,000 difference in mean samples for viewers response to the Annoyed question, we are attempting to answer is whether the show The Biggest Loser or The Apprentice: Los Angeles makes viewers annoyed. Based on this, The Apprentice: Los Angeles makes viewers more annoyed, on average, by a difference of 0.2709. We state with a 95% confidence interval, the difference in annoyance was typically between -0.5282 to -0.0239	 (The Biggest Loser - The Apprentice: Los Angeles). Because this confidence interval does not contain zero, we can say that the mean is statistically significant at the 5% level. 
```{r echo = FALSE, mesage = FALSE, include=FALSE}

loserApprentice <- pilotNBC %>% 
  filter( Show == "The Biggest Loser" | Show == "The Apprentice: Los Angeles")

mean(Q1_Annoyed ~ Show, data=loserApprentice)
diffmean(Q1_Annoyed ~ Show, data=loserApprentice)

bootAnnoyed = do(10000)*diffmean(Q1_Annoyed ~ Show, data=resample(loserApprentice))

confint(bootAnnoyed, level = .95)

```

```{r echo = FALSE, mesage = FALSE}
ggplot(bootAnnoyed) + 
  geom_histogram(aes(x=diffmean)) + labs( title = "Bootstrapped Confidence Interval: The Biggest Loser” & “The Apprentice: Los Angeles", x = "Difference in Means: Annoyed ")
```





### *Part C - “Dancing with the Stars” *

Using a bootstrapped 95% confidence interval of 10,000 proportion samples for viewers with a response of 4 or greater to the confusing question, we are attempting to find the true proportion of this response for the show Dancing with the Stars. The proportion on average for a response of 4 or greater to the confusing question is 0.0773 for Dancing with the Stars. We are 95% confident that the true population proportion a response of 4 or greater to the confusing question for Dancing with the Stars is somewhere between 0.0387 to	0.116. Because this confidence interval doesn’t contain zero, we can say that the proportion is statistically significant at the 5% level.

```{r echo = FALSE, mesage = FALSE, include=FALSE}

danceStars <- pilotNBC %>% 
  filter( Show == "Dancing with the Stars" )

danceStars = danceStars %>% 
  mutate(confuseAgree = ifelse(Q2_Confusing >= 4, yes = TRUE, no = FALSE))


prop(confuseAgree ~ Show, data=danceStars)

bootConfused = do(10000)*prop(~confuseAgree, data=resample(danceStars))

confint(bootConfused, level = .95)

```

```{r echo = FALSE, message = FALSE}
ggplot(bootConfused) + 
  geom_histogram(aes(x=prop_TRUE), bins= 27) + labs( title = "Bootstrapped Confidence Interval: Dancing with the Stars", x = "Difference in Means: Confusion ")
```



## *Problem 4:  Ebay* 
### *DMA Control Group minus DMA Treatment Group*

Your task is to compute the difference in revenue ratio between the treatment and control DMAs and provide a 95% confidence interval for the difference. Use these results to assess the evidence for whether the revenue ratio is the same in the treatment and control groups, or whether instead the data favors the idea that paid search advertising on Google creates extra revenue for EBay.


We are attempting to answer whether the revenue ratio is the same in the treatment and control groups, or whether instead the data favors the idea that paid search advertising on Google creates extra revenue for EBay using a 95% confidence interval of difference of means. The difference in revenue ratio (DMA Control Group minus DMA Treatment Group) is .0523. Our confidence interval for revenue ratio lays between 0.0908 to 0.013. The difference in average revenue ratio between DMA Control Group minus DMA Treatment Group is statistically significant at the 5% (0.05) level, because a 95% (0.95) confidence interval for that difference fails to contain zero.




```{r echo = FALSE, mesage = FALSE, include=FALSE}

mean(rev_ratio ~ adwords_pause, data=eBay)
diffmean(rev_ratio ~ adwords_pause, data=eBay)

bootRevRatio = do(10000)*diffmean(rev_ratio ~ adwords_pause, data=resample(eBay))

confint(bootRevRatio, level = .95)


```

```{r echo = FALSE, message = FALSE}
ggplot(bootRevRatio) + 
  geom_histogram(aes(x=diffmean)) + labs( title = "Bootstrapped Confidence Interval: DMA Control Group minus DMA Treatment Group", x = "Difference in Means: Revenue Ratio ")
```

